Appendix S1: Supporting Information

### 2021-09-06 ms/SI.Rmd
Load some latex packages in SI header to fix kable problem
fixes errror: "! Undefined control sequence. <recently read> \cellcolor"

see https://stackoverflow.com/questions/66522775/is-it-possible-to-rmarkdownrender-a-pdf-document-for-kable-tables-with-styling

---
title: "Appendix S1: Supporting Information"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

>>>>

---
title: "Appendix S1: Supporting Information"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
header-includes: 
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{colortbl}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---
